\documentclass[../lecture1-introduction.tex]{subfiles}

\begin{document}

\section{Editing, Compiling, and Execution}
% http://www-h.eng.cam.ac.uk/help/languages/C++/c++_tutorial/editing.html
% -------------------------------------------------------------------

\begin{frame}[fragile]{A Simple Program to Add Two Numbers}
    The following is an example of a simple program written in C++.
    % Animate this, first slide to guess what it does, second explains.
    The program is designed to read two numbers typed by a user at the keyboard;
    compute their sum and display the result on the screen.
\begin{cppcode}
// Program to add two integers typed by user at keyboard
#include <iostream>
using namespae std;

int main()
{
    int num1, num2, total;
    
    cout << "Enter integers to be added:" << endl;
    cin >> num1 >> num2;
    total = num1 + num2;
    cout << "The sum is " << total << endl;
    
    return 0;
}
\end{cppcode}
\end{frame}

% -------------------------------------------------------------------

\begin{frame}[fragile]{Program Structure and Syntax}
    C++ uses notation that may appear strange to non-programmers (and me).
    The notation is part of the programming language \texttt{syntax}.
    \begin{description}
        \item [Syntax] Formal rules that specify the structure of a legal program.
    \end{description}
\end{frame}

\begin{frame}[fragile]{Program Structure and Syntax}
    the notation and explanations which follow will appear strange if you have
    never written a computer program.

    Don't worry about them or how the program works. This will be explained
    in more detail later.

    The following is an overview.
\end{frame}

\begin{frame}[fragile]{Program Structure and Syntax}
    Every C++ program consists of a header and a main body and has the following
    structure:
%   \begin{minted}[linenos=true]{c++}
%   \end{minted}
\begin{cppcode}
// Comment statements which are ignored by computer
/* Also a comment */
#include < header file name >

int main()
{
    declaration of variables;
    statements;

    return 0;
}
\end{cppcode}
\end{frame}

\begin{frame}[fragile]{Program Structure and Syntax}
\begin{cppcode}
// Program to add two integers typed by user at keyboard
#include <iostream>
using namespae std;

int main()
{
    int num1, num2, total;
    
    cout << "Enter integers to be added:" << endl;
    cin >> num1 >> num2;
    total = num1 + num2;
    cout << "The sum is " << total << endl;
    
    return 0;
}
\end{cppcode}
    \only<1>
    {
        Line 1
        \begin{itemize}
            \item Lines beginning with // indicate that the rest of the line
            is a \textbf{comment}.
            \item Comments are inserted by programmers to help people read
            and understand the program.
            \item Can be placed anywhere in a program.
        \end{itemize}
    }
    \only<2>
    {
        Line 2
        \begin{itemize}
            \item Lines beginning with \# are instructions to the compiler's
            preprocessor.
            \item The \textbf{include} instruction says "what follows is a file name,
            find that file and insert its contents right here".
            \item Here the file iostream contains the definitions of
            \textbf{cin}, \textbf{cout}.
        \end{itemize}
    }
    \only<3>
    {
        Line 3
        \begin{itemize}
            \item Specifies that names used in the program (ie. \textbf{cin} and
            \textbf{cout}) are defined in the standard libraries.
            \item This is used to avoid problems with other libraries which may
            also use these names.
        \end{itemize}
    }
    \only<3>
    {
        Line 5
        \begin{itemize}
            \item When the program is executed the instructions will be executed
            in the oder they appear in the main body of the program.
            \item The main body is delimited by main() and the curly braces \{ \}
        \end{itemize}
    }
    \only<3>
    {
        Line 6
        \begin{itemize}
            \item Thing
        \end{itemize}
    }
    \only<3>
    {
        \begin{itemize}
            \item Thing
        \end{itemize}
    }
\end{frame}

% -------------------------------------------------------------------

\begin{frame}[fragile]{Development Environment \& Development Cycle}



\end{frame}

% -------------------------------------------------------------------

\end{document}
